\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-08-31 analysis/paper/paper.Rmd

```{r supportCB_abs, eval=eval_cs3, echo=TRUE, cache=TRUE}
# Estimating the absolute risk curve using the newdata parameter
newx <- model.matrix(death ~ . - d.time - aps - sps, 
                  data = test)[, -c(1)]
times <- sort(unique(test$d.time))

@@

ab <- rbind(abCB, abCN)
```

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} (A) Four curves comparing the probabilities of death as it changes over follow-up time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. All follow-up times seen in the new data were used to generate the curves. The Cox-based curves appear to be smooth, but this is due to the 1703 follow-up times seen while fitting the models and the 319 time points used to estimate the curves. (B) Four curves demonstrating the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. Lower is better. Penalized logistic regression produced the lowest Brier scores over follow-up time.", warning = FALSE}
# Compute Brier score for penalized models
brierFinalResults <- Score(list("Penalized Cox" = coxNet, "Penalized Logistic" = cbFull),
                           data = cbind(subset(test, select = c(d.time, death)),
                                        as.data.frame(newx)), 
                           formula = Hist(d.time, death != 0) ~ 1, summary = NULL, 
                           se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
#brierFinalResults$models<-as.character(brierFinalResults$models)
# Combine Brier scores between unpenalized and penalized models before plotting

>>>>

```{r supportCB_abs, eval=eval_cs3, echo=TRUE, cache=TRUE}
# Estimating the absolute risk curve using the newdata parameter
newx <- model.matrix(death ~ . - d.time - aps - sps, 
                  data = test)[, -c(1)]
times <- sort(unique(test$d.time))
#times<-seq(from=min(times),to=max(times),length.out = 100)

@@

ab <- rbind(abCB, abCN)

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} (A) Four curves comparing the probabilities of death as it changes over follow-up time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. All follow-up times seen in the new data were used to generate the penalized casebase and K-M curves. The Cox-based curves, estimated using the survival package, appear to be smooth because all 1703 follow-up times seen while fitting are used. Using user specified times is not permitted in the survival package. (B) Four curves demonstrating the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. Lower is better. Penalized logistic regression produced the lowest Brier scores over follow-up time.", warning = FALSE}
# Compute Brier score for penalized models
brierFinalResults <- Score(list("Penalized Cox" = coxNet, "Penalized Logistic" = cbFull),
                           data = cbind(subset(test, select = c(d.time, death)),
                                        as.data.frame(newx)), 
                           formula = Hist(d.time, death != 0) ~ 1, summary = NULL, 
                           se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
#brierFinalResults$models<-as.character(brierFinalResults$models)
# Combine Brier scores between unpenalized and penalized models before plotting

### 2020-08-31 analysis/paper/paper.tex

\begin{CodeInput}
R> # Estimating the absolute risk curve using the newdata parameter
R> newx <- model.matrix(death ~ . - d.time - aps - sps, 
R+                   data = test)[, -c(1)]
R> times <- sort(unique(test$d.time))
R> 
R> abCbFull <- casebase::absoluteRisk(cbFull,
R+   time = times,
R+   newdata = newx,
R+   s = "lambda.1se",
R+   method = "numerical"
R+ )
\end{CodeInput}
\end{CodeChunk}

Our first comparison plot examines the covariates that were selected
between all three hazard functions. Note that Cox regression without
penalization selected more covariates than the other two, but only the
intersection of coefficients with values greater than 0 are displayed in
\ref{fig:cs3lolliPlot}. A visible tendency is for Cox regression to have
larger estimated coefficients. This is expected, as there are no
restrictions on the size of coefficients. The smallest coefficient
estimates are found in penalized logistic model, aside from cancer state
(cano).

@@

\caption{\label{fig:cs3FinalBrier} (A) Four curves comparing the probabilities of death as it changes over follow-up time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. All follow-up times seen in the new data were used to generate the curves. The Cox-based curves appear to be smooth, but this is due to the 1703 follow-up times seen while fitting the models and the 319 time points used to estimate the curves. (B) Four curves demonstrating the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. Lower is better. Penalized logistic regression produced the lowest Brier scores over follow-up time.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

This report was generated on 2020-08-25 12:59:22 using the following
computational environment and dependencies:

>>>>

\begin{CodeInput}
R> # Estimating the absolute risk curve using the newdata parameter
R> newx <- model.matrix(death ~ . - d.time - aps - sps, 
R+                   data = test)[, -c(1)]
R> times <- sort(unique(test$d.time))
R> #times<-seq(from=min(times),to=max(times),length.out = 100)
R> 
R> abCbFull <- casebase::absoluteRisk(cbFull,
R+   time = times,
R+   newdata = newx,
R+   s = "lambda.1se",
R+   method = "numerical"
R+ )
\end{CodeInput}
\end{CodeChunk}

@@

\caption{\label{fig:cs3FinalBrier} (A) Four curves comparing the probabilities of death as it changes over follow-up time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. All follow-up times seen in the new data were used to generate the penalized casebase and K-M curves. The Cox-based curves, estimated using the survival package, appear to be smooth because all 1703 follow-up times seen while fitting are used. Using user specified times is not permitted in the survival package. (B) Four curves demonstrating the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. Lower is better. Penalized logistic regression produced the lowest Brier scores over follow-up time.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

This report was generated on 2020-08-25 15:21:11 using the following
computational environment and dependencies:
